comgen-outline

### 2017-07-03 paper/comgen-paper.Rmd
add errorsbars to habituals regression model plots

@@

d.hab.endorse.regression <- left_join(
  d.hab.endorsement.bayes,
  unique(select(
    d.hab.endorsement, habitual, logAnnualRate, time_period, mixture
  )) %>%
    mutate(regression_freq = predict(glm.hab.endorse.freq, ., type = "response"), 
           regression_freq_distinct = predict(glm.hab.endorse.freq.distinct, ., type = "response"))
) %>%
  gather(src, prediction, regression_freq, regression_freq_distinct) %>%
  mutate(sqErr = (MAP_h-prediction)^2)

@@

habituals.endorsement.models <- bind_rows(
  d.hab.endorse.regression %>% 
  mutate(prediction_lower = prediction,
         prediction_upper = prediction),
  left_join(
    m.hab.endorse.rsa %>% 
    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
    d.hab.endorse.regression %>% 
    select(habitual, time_period, logAnnualRate, mixture)
  )
) %>%
  mutate(src = factor(src, levels = c( 
                                      "habituals_model",
                                      "some_model",
                                      "regression_freq", 
                                      "regression_freq_distinct"
                                     ),
                      labels = c(
                                 "Speaker model - uncertain semantics",
                                 "Speaker model - fixed semantics",
                                 "Frequency alone", "Frequency + Distinctiveness"
                                 ))) %>%
  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(shape = 21)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 2)+
  theme(legend.position = "bottom")

>>>>

```{r}
d.gen.endorse.regression.prevalence <- left_join(
  d.gen.endorse.bayes,
  d.gen.endorse.prev.cue.uniq %>%
    mutate(
      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
    ) %>%
    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
) %>% mutate(
  sqErr = (MAP_h - prediction_mean) ^ 2
)

d.gen.endorse.regression <- bind_rows(
  d.gen.endorse.regression.prevalence.cuevalidity %>%
    mutate(src = "regression_Prev_Cuevalidity"),
  d.gen.endorse.regression.prevalence %>% 
    mutate(src = "regression_Prev")
  )
```

@@

d.hab.endorse.freq.mix.uniq <- unique(select(
    d.hab.endorsement, habitual, logAnnualRate, time_period, 
    mixture, mix_low, mix_high
  ))

d.hab.endorse.freq.mix.uniq.lower <- d.hab.endorse.freq.mix.uniq %>% 
  select(-mixture) %>% 
  rename(mixture = mix_low)

d.hab.endorse.freq.mix.uniq.upper <- d.hab.endorse.freq.mix.uniq %>% 
  select(-mixture) %>% 
  rename(mixture = mix_high)

d.hab.endorse.regression.freq <- left_join(
  d.hab.endorsement.bayes,
  d.hab.endorse.freq.mix.uniq %>%
    mutate(
      prediction = predict(glm.hab.endorse.freq, ., type = "response"), 
      prediction_lower = prediction,
      prediction_upper = prediction,
      src = "regression_freq"
      )
)

# n.b.: Since distinctiveness is being captured by "mix", the lower the "mix", the higher the endorsement. Thus, lower bound of errorbars are computed with upper estimate of "mix"
d.hab.endorse.regression.freq.mix <- left_join(
  d.hab.endorsement.bayes,
  d.hab.endorse.freq.mix.uniq %>%
    mutate(
      prediction = predict(glm.hab.endorse.freq.distinct, ., type = "response"),
      prediction_lower =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.upper, type = "response"),
      prediction_upper =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.lower, type = "response"),
      src = "regression_freq_distinct"
      )
)

d.hab.endorse.regression <- bind_rows(d.hab.endorse.regression.freq, d.hab.endorse.regression.freq.mix) %>%
  mutate(sqErr = (MAP_h-prediction)^2)

@@

habituals.endorsement.models <- bind_rows(
  d.hab.endorse.regression,
  left_join(
    m.hab.endorse.rsa %>% 
    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
    d.hab.endorse.regression %>% 
    select(habitual, time_period, logAnnualRate, mixture)
  )
) %>%
  mutate(src = factor(src, levels = c( 
                                      "habituals_model",
                                      "some_model",
                                      "regression_freq", 
                                      "regression_freq_distinct"
                                     ),
                      labels = c(
                                 "Speaker model - uncertain semantics",
                                 "Speaker model - fixed semantics",
                                 "Frequency alone", "Frequency + Distinctiveness"
                                 ))) %>%
  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(shape = 21)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 2)+
  theme(legend.position = "bottom")
```
